Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/intro.tex

We have implemented our algorithm on top of Matlab's multi-parametric toolbox 
for robust explicit MPC~\cite{matlabMPT}
and the Daisy tool for multi-precision tuning and fixed-point error analysis \cite{Daisy}.
We have applied our technique on a number of standard benchmark examples.
Our implementation finds that our mixed-precision implementation can save up to 20\% memory (on average, XXX\%) in controller
implementations over a uniform-precision implementation (and a saving of XXX\% over a uniform 32-bit implementation), while
maintaining the correctness of the controller.
In absolute terms, the saving corresponds to YYY KB over a uniform precision implementation on our largest benchmark.
In each case, the analysis takes only a few minutes of computation.
We also demonstrate the scalability of our mixed-precision tuning and error bounds analysis:
we show that on explicit MPC controllers with thousands of regions, our tool finishes in a few minutes\todo{Hours?}.

>>>>

We have implemented our algorithm on top of Matlab's multi-parametric toolbox 
for robust explicit MPC~\cite{matlabMPT}
and the Daisy tool for multi-precision tuning and fixed-point error analysis \cite{Daisy}.
We have applied our technique on a number of standard benchmark examples.
Our implementation finds that our mixed-precision implementation can save up to 20\% memory (on average, \RM{XXX}\%) in controller
implementations over a uniform-precision implementation (and a saving of \RM{XXX}\% over a uniform 32-bit implementation), while
maintaining the correctness of the controller.
In absolute terms, the saving corresponds to \RM{YYY} KB over a uniform precision implementation on our largest benchmark.
In each case, the analysis takes only a few minutes of computation.
We also demonstrate the scalability of our mixed-precision tuning and error bounds analysis:
we show that on explicit MPC controllers with thousands of regions, our tool finishes in a few minutes\todo{Hours?}.

We summarize our contributions.
\begin{itemize}
\item We provide an end-to-end tuning algorithm for robust explicit MPC;
\item We design a static and scalable error analysis algorithm for piecewise affine functions;
\item Through a set of standard control benchmarks, we demonstrate that our tuning algorithm
can achieve up to 20\% savings in memory while maintaining robustness.
\end{itemize}
